Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/testing.tex
Revise test section

Four common mistakes in specifications have been observed: contradictions, vacuity, under-specification, and missed corner cases.
Contradictions arise from inconsistent contracts that state conflicting constraints in any given moment invalidating the verification results.
Vacuity is a common pitfall with implication when the left hand side is always false making the implication true. 
Under-specification is very challenging because verification is not able to prove anything (or it can prove everything in the case of existential properties) so nothing is actually known after verification except that the system is under-specified. 
Missed corner cases is a common problem to all disciplines.
It is especially hard here because there is no direct way to provide test input and check test output.

AGREE already detects, and reports, contradicting and inconsistent contracts, but it does not check for vacuity and under-specification.
The tempting approach to check these issues is to use the synthesis path and then apply traditional testing.
Such an approach adds extra steps that are not needed, as it is
possible to bridge the formal model in AGREE, with its proof system, to
traditional validation using tests.

@@

\figref{fig:test} is a unit test for the high-assurance monitor in \figref{fig:hardened}.
The test checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm does not fire.
\lineref{line:tst-index} creates an index to use to create the test input.
\lineref{line:tst-assume-1} defines when the response appears relative to the index.
\lineref{line:tst-assume-2} defines the request behavior.
\linesref{line:tst-guarantee-1}{line:tst-guarantee-2} define the expected test output.
The test additionally proves that nothing happens after the initial test input and output (e.g., no more input is provided and no more output is generated).
AGREE proves the test correct.
\linesref{line:tst-imp-start}{line:tst-imp-end} implement the system using the component (\lineref{line:tst-imp-comp}).
\figref{fig:test-output} is the AGREE output for the test, showing that it passes.

>>>>

There are three common mistakes in specifications, aside from self-consistency that is already checked, that have been observed: vacuity, under-specification, and missed corner cases.
Vacuity is a common pitfall with implication when the left hand side is always false making the implication true. 
Under-specification is very challenging because verification is not able to prove anything (or it can prove everything in the case of existential properties) so nothing is actually known after verification except that the system is under-specified. 
Missed corner cases is a common problem to all disciplines.
It is especially hard here because there is no direct way to provide test input and check test output.

The tempting approach is to use the synthesis path to check these issues with traditional testing.
Such an approach adds extra steps that are not needed, as it is
possible to bridge the formal model in AGREE, with its proof system, to
traditional validation using tests.
The key is to consider the component as implementing a test specification.

@@

\figref{fig:test} is a unit test for the high-assurance monitor in \figref{fig:hardened}.
The test checks if the monitor output coincides with the response that comes one step after the request.
It also checks that the alarm does not fire.
\begin{compactitem}
\item \lineref{line:tst-index}. An index to use to define the test input and expected test output through time.
\item \lineref{line:tst-assume-1} and \lineref{line:tst-assume-2}. The test input. These define when the request and response message events should appear relative to the index.
\item \lineref{line:tst-guarantee-1} and \lineref{line:tst-guarantee-2}. The expected test output. 
The test additionally proves that nothing happens after the initial test input and expected output, \ie, no more input is provided and no more output is generated.
\item \linesref{line:tst-imp-start}{line:tst-imp-end}. The implementation with the component under test (\lineref{line:tst-imp-comp}).
\end{compactitem}
\figref{fig:test-output} is the AGREE output for the test, showing that it passes.
